Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-06-18 paper/tex/sections/discussion.tex
new subsection on simple MW
fix typos

Overall, combining these methods we find that for a 4(10)-year mission, LISA will detect at least 15(22) BHBHs, 12(18) BHNSs and 19(27) NSNSs that are distinguishable from the WDWD population.

@@

The problem of separating the BHBH, BHNS and NSNS population can be more difficult. We can follow a similar method to the WDWDs (see Sec.~\ref{sec:WDWD_distinguish}) by applying our knowledge of the maximum mass of a neutron star. Following our fiducial assumption, we can take the maximum mass of a neutron star as $2.5 \unit{M_{\odot}}$ and thus the maximum chirp mass that a system can attain without one of the components being a black hole is $\mathcal{M}_{c} = 2.2 \unit{M_\odot}$. For a 4(10)-year LISA mission, the fraction of systems that are above or below this limit by more than $2 \Delta \mathcal{M}_c$ is 15(20)\% for BHBHs, 12(14)\% for BHNSs and 34(40)\% of NSNSs, which in terms of absolute detections is 5(11) for BHBHs, 4(8) for BHNSs and 11(21) for NSNSs. For separating the BHBH and BHNS population one could consider the range of mass ratios that could result in the chirp mass and assume that those that are likely close to unity must be BHBHs.

@@

>>>>

Overall, combining these methods we find that for a 4(10)-year mission, LISA will detect at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs that are distinguishable from the WDWD population.

@@

The problem of separating the BHBH, BHNS and NSNS population can be more difficult. We can follow a similar method to the WDWDs (see Sec.~\ref{sec:WDWD_distinguish}) by applying our knowledge of the maximum mass of a neutron star. Following our fiducial assumption, we can take the maximum mass of a neutron star as $2.5 \unit{M_{\odot}}$ and thus the maximum chirp mass that a system can attain without one of the components being a black hole is $\mathcal{M}_{c} = 2.2 \unit{M_\odot}$. For a 4(10)-year LISA mission, the fraction of systems that are above or below this limit by more than $2 \Delta \mathcal{M}_c$ is 15(20)\% for BHBHs, 12(14)\% for BHNSs and 34(40)\% of NSNSs, which in terms of absolute detections is \BHBHDistinguishedFour{}(\BHBHDistinguishedTen{}) for BHBHs, \BHNSDistinguishedFour{}(\BHNSDistinguishedTen{}) for BHNSs and \NSNSDistinguishedFour{}(\NSNSDistinguishedTen{}) for NSNSs. For separating the BHBH and BHNS population one could consider the range of mass ratios that could result in the chirp mass and assume that those that are likely close to unity must be BHBHs.

@@

\subsection{Assessing the effect of an improved Milky Way model}
\tom{I'm going to run everything with a simple model (maybe copy Breivik+2020) and see how the results change.}
